\begin{titlingpage}
\vspace*{\fill}
\begin{center}
\setlength{\fboxrule}{2pt}
\fbox{
\crdfontfamily
\parbox[b][][c]{0.9\textwidth}{
\parbox[t][][t]{0.9\textwidth}{\Large \center \textbf{Northeast Fisheries Science Center Reference Documents}}\\[4ex]

\parbox[c][][c]{0.9\textwidth}{
\textbf{This series is a secondary scientific series} designed to assure the long-term documentation and
to enable the timely transmission of research results by Center and/or non-Center researchers,
where such results bear upon the research mission of the Center (see the outside back cover for
the mission statement). These documents receive internal scientific review, and most receive
copy editing. The National Marine Fisheries Service does not endorse any proprietary material,
process, or product mentioned in these documents.\vspace{6pt}

All documents issued in this series since April 2001, and several documents issued prior to
that date, have been copublished in both paper and electronic versions. To access the electronic
version of a document in this series, go to http://www.nefsc.noaa.gov/nefsc/publications/. The
electronic version is available in PDF format to permit printing of a paper copy directly from
the Internet. If you do not have Internet access, or if a desired document is one of the pre-April
2001 documents available only in the paper version, you can obtain a paper copy by contacting
the senior Center author of the desired document. Refer to the title page of the document for
the senior Center author's name and mailing address. If there is no Center author, or if there is
corporate (i.e., non-individualized) authorship, then contact the Center's Woods Hole Laboratory
Library (166 Water St., Woods Hole, MA 02543-1026).
\vspace{6pt}

\textbf{Information Quality Act Compliance}: In accordance with section 515 of Public Law 106-
554, the Northeast Fisheries Science Center completed both technical and policy reviews for
this report. These predissemination reviews are on file at the NEFSC Editorial Office.
This document may be cited as:

\vspace*{7ex}
\begin{center}
\parbox[c][][c]{0.7\textwidth}{\small \crdciteas}
\end{center}
\vspace*{7ex}

}}
}
%\end{minipage}
\end{center}
\end{titlingpage}
